Species motif participation provides unique information about species risk of extinction

### 2023-04-27 manuscript/reorder_main_text.tex
one spelling error

        The relationships between other motifs and persistence were more consistent over different levels of connectance and network size.
        Slopes of the motif proportion-persistence relationships for the apparent compeition and direct competition motifs were steepest in large and less-connected networks but the directions of slopes varied only with the strength of disturbance, as in Fig.~\ref{Fig 2}.
        The relationship between proportion of the three-species chain in the participation vector and persistence was very similar across all levels of size and connectance.

>>>>

        The relationships between other motifs and persistence were more consistent over different levels of connectance and network size.
        Slopes of the motif proportion-persistence relationships for the apparent competition and direct competition motifs were steepest in large and less-connected networks but the directions of slopes varied only with the strength of disturbance, as in Fig.~\ref{Fig 2}.
        The relationship between proportion of the three-species chain in the participation vector and persistence was very similar across all levels of size and connectance.
